% ved ikke om der skal skrive mere på
\section{Grammar}
There are 4(0-3) types of grammar, where type 0 is the more unrestricted and type 3 is the more restricted grammar.

\subsection{Type - 3: Regular Grammar}
Regular grammar are describe by finite automate that again is use to recognize regular language. Regular Grammar are good to use on computer extremely limited amount of memory. Since regular language do not need to use a lot of memory to recognize language. but there are some language that Regular grammar can not recognize.

\subsection{Type - 2: Context-Free Grammar}
Context-free grammar are describe by substitution rules, also called productions, and pushdown automata with are use to describe context-free languages.

With substitution rules there can chance that a language that are ambiguous. this can be a problem since different computers might make different output with the same substitution rules.

Pushdown automata work almost the same as a finite automate the big main differences is. That pushdown automata use a memory stack to help make the output.

\subsection{Type - 1: Context-Sensitive Grammar}
Context-sensitive grammar are nearly the same as substitution rules use in Context-free grammar, but here the rules can also include the terminals on both sides of the termination.

\subsection{Type - 0: Recursively Enumerable}
Recursively enumerable or unrestricted grammar is where there is no restrictions on the left and right sides of the grammar's productions.
% kommer hvist i kapitel 3 i Syntaks og semantik hvor det hedder Turing-recognizable

\subsection{choice of Grammar}
The grammar that have been use to describe the language for the  project compiler is context-free grammar. Because it is relatively easily to understand a language describe in context-free grammar, but still strict enough that a computer can work with it. Another reason for using context-free grammar is that most parsers and lexers generator use BNF (Backus–Naur Form) or EBNF (Extended Backus–Naur Form) that is a notation form for context-free grammar