\section{Type checking}
In this section we will describe how we type check code using the visitor pattern from the pretty printer \fxfatal{ref mangler}.

\subsection*{Value}
We use a class called "Value" to be able to return almost any type of data through the visitor pattern.
\kode{Value type}{Value}{Value.txt}
This class as can be seen on listing \ref{lst:Value} allows us to write "Value p = new Value(5)" thus we can return the value 5 up our tree. This can also be used to combine different types into a string and return them as a value. This is useful because we do not always know what type will be returned and this makes it possible to convert everything into the same type which we can evaluate later.
\kode{How to evaluate Value}{isType}{isType.txt}
When we evaluate the type value we could use functions like those seen on listing \ref{lst:isType} which returns "true" or "false". In the code example we make use of regular expressions to determine if it is an int or double if it contains numbers and symbols in the defined order. We use similar functions for each other type we have in the language.

\subsection*{Container and drink}


\subsection*{Functions}
The code that programmer writes is intended to be compiled to an Arduino platform and as such needs to have certain functions to work properly, such as a function "setup" and "loop" and thus we check if they are present. But some commands like LCDPrint and RFIDWrite are predefined in the Arduino language and can be used without a declaration, so we have also defined them in our language like seen on listing \ref{lst:LCDPrint}
\kode{Defining LCDPrint}{LCDPrint}{LCDPrint.txt}
We will not implement all Arduino functions because it would take too much time and effort, so we have decided to only take the ones involved with the LCD and RFID. Furthermore we have defined our own function \ref{lst:PourDrink} so we can type check it.
\kode{Predefining function PourDrink}{PourDrink}{PourDrink.txt}

\subsection*{Variables}
In our language "INPUT" and "OUTPUT" would be seen as variables and by default be undefined so we predefined them like seen on listing \ref{lst:OUTPUT}. This is also done for "A0" to "A5" since these are used when determining input and output for the Arduino board, we have defined them with the type "container".
\kode{Predefining OUTPUT}{OUTPUT}{OUTPUT.txt} 
