\chapter{Our Language}
We have discussed the syntax of our new language, and have written a draft to how we want the control statements and operators to look like in the new language.

The "..." is a placeholder for an input, expression or statement.

First we have the "if"-statement.
if (...)
Begin
	if (...)
	begin
		...;
	end
	else if (...)
	begin
		...;
	end
	else
	begin
	...
	end
end

This is how we want the "while"-loop look like.
while (...)
begin
	...;
	...;
	...;
end
	
This is how we imagine the "for"-loop is going to look like.
from ... to ... step ...
begin
	...;
	...;
	...;
end

This is the "switch"-statement in our language.
switch (...)
begin
	Case 4:
		call DoSomething();
		Break;
	Case 8:
		call DoSomethingElse();
		Break;
	Default:
		call DoSomethingElseAgain();
	Break;
end

This is an example of a function "Serve", which returns an int.
function Serve returns int using (...)
begin
	...;
	...;
	...;
	return 4;
end

And this is how we would like to call our functions.
call Serve (...);

This is the types we want implemented
\textit{TYPES:}
double
int
string
bool
array->Drink

Here is the operators from C\# and what our language will have instead. A "~~~" means we do not want it implemented.
C\#	|	Our
============
=  	|	<--
==	|	=
+	|	+
+=	|	~~~
-	|	-
-=	|	~~~
*	|	*
*=	|	~~~
/	|	/
/=	|	~~~
<=	|	<=
>=	|	>=
&&	|	AND
||	|	OR
\%	|	~~~
++	|	?
--	|	?
;	|	;
<	|	<
>	|	>
!	|	!

%Hvad vi gerne vil have i et sprog
%Object-Oriented
%Declared methods
%Readable
%Compilation
%Writable
%Orthogonality
%Documentation

Name:

SPLAT - Simple Programming Language for Arduino Tipple-mixer


(Just an idea for a name for our language)




%Container Vodka = 14;

%Call pour(Vodka, 2)

%Function Pour returns bool using(container, quantity)
%Begin
%	...
%End

Functions that need to be implemented before they can compile the program.

Pour
Serve
Setup
MakeDrink(int id)
======
Optional functions that can be implented

Shake
Stir
Ice
======
These are the functions already implemented in the language.

Output
Input

%Skal print virkelig ligge her?								Og det her hvor skal det være?
function print returns nothing using(LCD y, string x)     (int[] LCD)
begin
	...
end