\chapter{Our Language}
We have discussed the syntax of our new language, and have written an outcast to how we want the the control statements and operates to look like in the new language.

The "..." means some input, expression or statement is left out.

First we have the "if"-statement.
if (...)
Begin
	if (...)
	Begin
		...;
	End
	Else if (...)
	Begin
		...;
	End
	Else
	Begin
	...
	End
End

This is how we want the "while"-loop look like.
While (...)
Begin
	...;
	...;
	...;
End
	
This is how we imagine the "for"-loop is going to look like.
From ... To ... Step ...
Begin
	...;
	...;
	...;
End

This is the "switch"-statement in our language.
Switch (...)
Begin
	Case 4:
		DoSomething();
		Break;
	Case 8:
		DoSomethingElse();
		Break;
	Default:
		DoSomethingElseAgain();
	Break;
End

This is an example of a function "Serve", which returns an int.
Function Serve returns int using (...)
Begin
	...;
	...;
	...;
	return 4;
End

And this is how we would like to call our functions.
Call Serve (...);

This is the types we want implemented
\textit{TYPES:}
double
int
string
bool
array->Drink

Here is the operators from C\# and what our language will have instead. A "~~~" means we do not want it implemented.
C\#	|	Our
============
=  	|	<--
==	|	=
+	|	+
+=	|	~~~
-	|	-
-=	|	~~~
*	|	*
*=	|	~~~
/	|	/
/=	|	~~~
<=	|	<=
>=	|	>=
&&	|	AND
||	|	OR
\%	|	~~~
++	|	?
--	|	?
;	|	;
<	|	<
>	|	>
!	|	!

%Hvad vi gerne vil have i et sprog
%Object-Oriented
%Declared methods
%Readable
%Compilation
%Writable
%Orthogonality
%Documentation

Name:

SPLAT - Simple Programming Language for Arduino Tipple-mixer


(Just an idea for a name for our language)




%Container Vodka = 14;

%Call pour(Vodka, 2)

%Function Pour returns bool using(container, quantity)
%Begin
%	...
%End

These are the functions that the user will need to implement before compiling the program.

Pour
Serve
Ice
Shake
Stir
Setup
MakeDrink(int id)
======
These are the functions already implemented in the language.

Output
Input
Function print returns nothing using(LCD y, string x)     (int[] LCD)
Begin
	...
End