\section{Discussion}
in this section there will be debate if the goals have been reached and there after a perspective of the rapport is made

\subsection{Characteristic of a compiler}
If one look at the characteristic of a compiler we can is if our compiler hold up to what we have chosen.

"Simplicity" was set to be high for our language. This have been achieved since SPLAD have a few ways to make complex functions and statements

% lav kode eksempler til hvordan der ser ud med vores og arudinuo

"Orthogonality" was set to be medium for our language. Since it is  not possible to make classes or constructs in our language, but one can call a function in an expression.

"Data types" was set to be medium for our language. Because we only have five primitive types and two special types, our language have few types, but still not a lot of types. Thereby this characteristic \fxfatal{kan ikke finde den rigtige bøjning} have been achieved.

"Syntax design" was set to be high for our language. Since most of our language have been made in the way to be better understood what a "for loop" do and where block start and ends. Therefore have this characteristic \fxfatal{kan ikke finde den rigtige bøjning} been achieved in our programming language.

"Support for abstraction" was set to be medium for our language. 

"Expressivity" was set to be low for our language.

"Type checking" was set to be high for our language.

"Exception handling" was set to be low for our language.

"Restricted aliasing" was set to be low for our language.

