\subsection{Simplicity of SPALD compared with C}
This section will compare pieces of code written in SPLAD, with pieces of code written in C. The first code example, seen on listring \ref{lst:helloworldsplad}, is an example of a simple SPLAD program, which prints out "HelloWorld" to the LCD.

\begin{code}{helloworldsplad}{Hello world program in SPLAD}
\begin{lstlisting}
function pour return nothing using(int a, double b)
begin
	return nothing;
end

function RFIDFound return nothing using(int a, int b)
begin
	string message <-- "Hello World!";
	/* Print message on line 1 on LCD */
	call LCDPrint(message, 1);

	return nothing;
end
\end{lstlisting}
\end{code}

Line 1-4 of \ref{lst:helloworldsplad} contains the pour function, which is required by the SPLAD compiler, but is not relevant in this small example. The string "message" is declared on line 7, which is what will be printed to the LCD. On line 9, the function LCDPrint, which is provided by the SPLAD compiler is called, and the message is printed to the display. The message will be printed when an RFID-tag is found by the RFID-reader.

A hello world program written in Arudino C/C++, can be seen on listing \ref{lst:helloworldc}. It should be noted that this is an example provided by the Arduino IDE \citep{LCDtut}. Line 2 of this example includes the LCD Library. On line 5 the LCD display must be initialized with the pins on the Arduino. On line 9, the LCD display is setup, which means that the appropriate number of columns and rows is set depending on the particular model used. At last on line 11, the message is printed to the LCD.
 
\begin{code}{helloworldc}{Hello world program in Arduino C/C++}
\begin{lstlisting}
// include the library code:
#include <LiquidCrystal.h>

// initialize the library with the numbers of the interface pins
LiquidCrystal lcd(12, 11, 5, 4, 3, 2);

void setup() {
  // set up the LCD's number of columns and rows: 
  lcd.begin(16, 2);
  char message[ ] = "Hello World";
  // Print a message to the LCD.
  lcd.print(message);
}

void loop() {

}
\end{lstlisting}
\end{code}
The difference between the SPLAD program, and the Arduino program is clear: The SPLAD program is much more specialized with the target being drinks machine, which means that there is an LCD print function provided by default. This is not the case in a normal Arduino program, because the Arduino is aimed much more at general purpose. This means that users of the SPALD language need not think about which pins the LCD is connected to while writing programs. The Arduino does not provide a string-type, which means that strings are implemented by char arrays. In the SPLAD language there is a string type, which might seem more intuitive for novice programmers. The assignment is a bit different in SPLAD compared to C-notation. In SPLAD an assignment is denoted by '<--', which makes it completely clear what is assigned to what. In C, the assignment is denoted by '=', which might confuse novice programmers, because '=' generally is used to denote equality in for example mathematics. Also when using the '=', it is not really clear what is assigned to what.