\section{Evaluation Criteria for the Compiler}
To express the priorities of this project, we use a table, see table \ref{tab:criteria} where we rate each criteria by the importance compared to the other.

\begin{table}
\begin{tabular}{ c | c | c | c | c |}
\textbf{Criteria} & \rotatebox{90}{Very Important} & \rotatebox{90}{Important} & \rotatebox{90}{Less Important} & \rotatebox{90}{Irrelevant}\\ \hline
Reliable      		& $\bullet$ &   &   &       \\ \hline
Effectiveness       &   &   & $\bullet$ &       \\ \hline
Correctness         & $\bullet$ &   &   &       \\ \hline
Testable        	&   &   & $\bullet$ &        \\ \hline
Maintainable		&   &   & $\bullet$ &        \\ \hline
Moveable        	&   & $\bullet $&   &        \\ \hline
Recycle     		&   &   &   &$ \bullet$      \\ \hline
Safe         		&   &   &   &$ \bullet $     \\ \hline

\end{tabular}
\caption{This table will be used to prioritize the different criteria compared to the compiler in this project.}
\label{tab:criteria}
\end{table}

We want the compiler and its output to be as reliable as possible because the compiler should not generate errors on its own. The programmer should be able to write a correct program, compile it and be able to run it, hence we do not want the compiler to be a source of errors. Therefore, we have prioritized the criteria "reliable" as very important.

The effectiveness of the compiler is not as important as the functionality of the compiler. We have decided that effectiveness should not be in focus, based on the idea that the compiler will run on modern computers and is aimed at hobby programming. Therefore the effectiveness is rated as less important compared to the other criteria.

The compiler should fulfill the given criterion to achieve the properties set for the compiler of this project. Therefore, we have set the "correctness" criterion as very important.

We have estimated that we should be able to test the compiler to check its correctness but we do not estimate the "testable" criterion as important as other properties. Therefore, it has been rated as less important.

Because the compiler is meant as a product, the focus has not been to simplify the compiler so it is easier to maintain. This would be attractive if the compiler should be used for further development later but that is not the case. Therefore, we have rated "maintainable" as less important.

We want the compiler to be able to run on as many operating systems as possible, so the users are not restricted by their systems. The compiler is written in Java, which makes it able to run on different operating systems as long as the Java virtual machine is implemented for their architecture. Therefore, we have rated the "moveable" criterion as important.

The "recycle" criterion has been rated as irrelevant, because its not in the intention to make parts of the compiler usable out of the context. Meaning different parts of the compiler is context dependent.

We have also rated the "safe" criterion as irrelevant because this compiler does not handle security critical data.