\section{Discussion}
\label{sec:discussion}
in this section there will be debate if the goals have been reached and there after a perspective of the rapport is made

\subsection{Characteristic of our language}
If one look at the characteristic of a compiler we can is if our compiler hold up to what we have chosen.

"Simplicity" was set to be high for our language. This have been achieved since SPLAD have a few ways to make complex functions and statements

"Orthogonality" was set to be medium for our language. Since it is  not possible to make classes or constructs in our language. But it is possible to call a function in an expression. Therefore we think that we have achieved this characteristic \fxfatal{kan ikke finde den rigtige bøjning} at the level we what it to be.

"Data types" was set to be medium for our language. Because we only have five primitive types and two special types, our language have many types, but still not that many types which makes it easily to have an overview them, and it is not possible to make classes or constructs. Thereby this characteristic \fxfatal{kan ikke finde den rigtige bøjning} have been achieved.

"Syntax design" was set to be high for our language. Since most of our language have been made in the way to be better understood what a "for loop" do and where block start and ends. Therefore have this characteristic \fxfatal{kan ikke finde den rigtige bøjning} been achieved in our programming language.

"Support for abstraction" was set to be medium for our language. Because our language is an abstraction in itself. There is particular form for abstraction in our language. But in our language it is not possible to do abstraction. This limit in our language is for helping beginners to get a easier and faster understanding of a given code in our language.

"Expressivity" was set to be low for our language. Since our language had it focus to be as simple as possible, are expressivity not done in our language. 


"Type checking" was set to be high for our language. To make sure that all type errors could be find is fund when a program is compiled. Therefore a lot of work and tests have been into the type checker. There were a some problems, like the build-in functions that a Arduino board have. This make it hard to make a type checker that are will find all errors. But all the types, expressions, parameters that are in our language are type check and therefore have this 


