\subsection{Conclusion}
This section concludes the report, and contains a round up of the most important aspects of the project.
The problem statement was presented in section \ref{sec:problemstatement}, and is as follows: 
\begin{itemize}
	\item \textbf{How can a programming language be developed, which makes it suitable for the hobby programmer to program drink machines based on Arduino platforms?}
\end{itemize}

To answer the problem statement, the SPLAD language was developed, which aimed at being a programming language that less experienced- and hobby programmers could program in. The formal specification of the SPLAD language can be seen in chapter \ref{chap:lanspec}. The SPLAD language is an abstraction of the C/C++ like language used for programming for the Arduino platform. The abstraction enables the programming of a drinks machine with less effort than if it was programmed directly in the Arduino language, this is discussed more thoroughly in \ref{sec:discussion} \fxfatal{lav label i diskussion når den færdig}. The main focus of the problem statement is, how a programming language suitable for a novice programmer can be specified.

This has been done by only including simple constructs, and not support more writeable statements, such as "i++" or "?" instead of "if else". This was decided to heighten readability, at the expense of decreasing writeability. These decisions and the trade offs between the different criteria can be seen in section \ref{sec:designcriteria}. Another design decision that was made to heighten readability at the cost of writeability was the assignment of values to variables. In SPLAD this is denoted by "x <-- 4", where most other programming languages simply allows "x = 4". This decision removes any doubt about what is assigned to what. These decisions makes the SPLAD language more suitable for novice programmers.
Another part of developing a programming language, is making a compiler for the language. This process can be seen in chapter \ref{chap:implementation}. The parser and lexical analyzer (lexer) of the SPLAD compiler is generated by ANTLR, which is a lexer and parser generator. The parser and lexer generates a parse tree, which is given to the type checker, which decorates this tree with types. At last the code generator generates the target code, which can then be further compiled by the Arduino compiler. This answers the second sub-statement of the problem statement. Therefore it can be concluded, that this project fulfills the problem statement. 