\subsection{Informal Type Rules}
This section contains the informal type rules. In the type rules, $E$ is an expression and $S$ is a statement.
\begin{itemize}
\item Type rule for \textbf{<, >, <=, >=} :

"$E_1$ (<, >, <=, >=) $E_2$" is type correct and of type boolean if $E_1$ and $E_2$ are type correct and of type integer or double.

\item Type rule for \textbf{!=, =} :

"$E_1$ (!=, =) $E_2$" is type correct and of type boolean if $E_1$ and $E_2$ are type correct and of type integer or double, or if $E_1$ and $E_2$ are of the same type of either char, bool or string.

\item Type rule for \textbf{+} :

"$E_1$ (+) $E_2$" is type correct and of type integer, string or double if $E_1$ and $E_2$ are type correct and of type integer, string or double.

\item Type rule for \textbf{-, *} :

"$E_1$ (-, *) $E_2$" is type correct and of type integer or double if $E_1$ and $E_2$ are type correct and of type integer or double.


\item Type rule for \textbf{/} :

"$E_1$ / $E_2$" is type correct and of type double if $E_1$ and $E_2$ are type correct and of type integer or double.

\item Type rule for \textbf{<-\,-} (assign) :

"$E_1$ <-\,- $E_2$" is type correct if $E_1$ and $E_2$ are type correct and $E_1$ and $E_2$ are of the same of type or if $E_1$ and $E_2$ is of type integer or double.

\item Type rule of 'while'-statement: 

"while ($E$) begin $S$ end" is type correct if $E$ is of type boolean and type correct and $S$ is type correct.

\item Type rule of 'from to step'-statement: 

"from $E_1$ to $E_2$ step $E_3$ begin $S$ end" are type correct if $E_1$, $E_2$ and $E_3$ are type correct and of type integer, and $S$ is type correct.

\item This is the type rules for 'if-else'-statement:

"if($E$) begin $S_1$ end else $S_2$" is type correct if $E$ is type correct and of type boolean, and $S_1$ and $S_2$ is type correct.

\item Here the type rules for switch/case is described:

"switch ($E$) begin case $E_1$: $S_1$ break; ... case $E_n$: $S_n$ break; default: $S_d$ break; end" is type correct if $E$, $E_1$...$E_n$ are type correct and of type integer, bool, double, char or string and are of the same type, and $S_1$...$S_n$ and $S_d$ are type correct.
\end{itemize}