% ved ikke om der skal skrive mere på - Niels
\section{Grammar}
There are 4(0-3) types of grammar, where type 0 is the more unrestricted and type 3 is the more restricted grammar.

\subsection{Type - 3: Regular Grammar}
Regular grammar are describe by finite automate that again is use to recognize regular language. Regular Grammar are good to use on computers with extremely limited amount of memory, since regular language do not need to use a lot of memory to recognize language. But there are some language that Regular grammar can not recognize.

\subsection{Type - 2: Context-Free Grammar}
Context-free grammar are describe by substitution rules, also called productions, and pushdown automata which are use to describe context-free languages.

With substitution rules for Context-Free Grammar can have chance for a ambiguous languages.
%hvad mener du i linjen herover? 
This can be a problem since different computers might make different output with the same substitution rules.

Pushdown automata work almost the same as a finite automate the big main differences is, that pushdown automata use a memory stack to help make the output.

\subsection{Type - 1: Context-Sensitive Grammar}
Context-sensitive grammars substitution rules have nearly the same rules as those that are use in Context-free grammar.
% læs sætningen over igen da den ikke giver mening. Du skriver at den kontekt-sensetive grammatik næsten er det samme som substitution reglerne der bliver brugt i den kontekst frie grammatik.
But with Context-Sensitive the right side of the production can have more then one terminal and there can be non-terminals on the right side of the production
%Læs det hele her igen.

\subsection{Type - 0: Recursively Enumerable}
Recursively enumerable or unrestricted grammar is where there is no restrictions on the left and right sides of the grammar's productions.
% kommer hvist i kapitel 3 i Syntaks og semantik hvor det hedder Turing-recognizable
%Kommer vist? hvor har du så fundet informationen ?
%står i bogen på side 170 forneden at "Turing-recognizable" bliver kaldt for "recursively enumerable language" i andre bøger
\subsection{choice of Grammar}
The grammar that have been use to describe the language for the  project compiler is context-free grammar. It is relatively easily to understand a language described in context-free grammar, but it is still strict enough that a computer can work with it. Another reason for using context-free grammar is that most parsers and lexers generator use BNF (Backus–Naur Form) or EBNF (Extended Backus–Naur Form) that is a notation form for context-free grammar