\subsection{Type Rules} % er blevet lavet itemize for at bedre kunne få et overblik over typereglerne
This section contains the type rules for the comparison operator.
\begin{itemize}

\item Type rule for \textbf{<, > <=, >=}:

"$E_1$ (<, > <=, >=) $E_2$" is type correct and of type boolean if $E_1$ and $E_2$ are type correct and of type integer, double.

\item Type rule for \textbf{!=, =}:

"$E_1$ (!=, =) $E_2$" is type correct and of type boolean if $E_1$ and $E_2$ are type correct and of type integer, double, or if $E_1$ and $E_2$ are of the same type of either char or string.

\item Type rule for \textbf{+, -, *}:

"$E_1$ (+, -, *) $E_2$" is type correct and of type integer or double if $E_1$ and $E_2$ are type correct and of type integer or double.

\item Type rule for \textbf{/}:

"$E_1$ (/) $E_2$" is type correct and of type integer or double if $E_1$ and $E_2$ are type correct and of type integer or double and $E_2$ does not have the value of zero.

\item Here the type rules of assign will be described:

"$E_1$ <-- $E_2$" is type correct if $E_1$ and $E_2$ are of the same of type integer, double, char or string.

\item Here the type rules of loops will be described.

\item Type rule of 'while'-statement: 
"while E begin C end" is type correct if E of type boolean and C are type correct.

\item Type rule of 'from to'-statement: 

"from $E_1$ to $E_2$ begin C end" are type correct if $E_1$ and $E_2$ are type correct and of type integer, and C are type correct.

\item This is the type rules for 'if'-statement:

"if(E) begin C end" is type correct if E are type correct and of type boolean, and C are type correct.

\item Here the type rules for switch/case will be described:

"switch (E) begin case $E_1$: $C_1$ break; ... case $E_n$: $C_n$ break; default: $C_d$ break; end" is type correct if E, $E_1$...$E_n$ are type correct and of type integer, double, char or string and are the same type, and $C_1$...$C_n$ and $C_d$ are type correct.
\end{itemize}